---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# anime

<!-- badges: start -->
<!-- badges: end -->

The goal of anime is to join the attributes of two spatial datasets based on the amount of overlap between their linestrings.

## Installation

You can install the development version of anime from [GitHub](https://github.com/) with:

```{r}
#| eval: false
# install.packages("pak")
pak::pak("JosiahParry/anime/r")
```

```{r}
library(anime)
```

## Local development

To develop the R package, clone the repo, open R in the r directory and run the following to load a locally installed version:

```{r}
#| eval: false
devtools::load_all()
```

## Basic example

`anime` uses the concept of a `target` and `source` linestrings. 

`target` linestrings are matched _to_ the `source` linestrings. The amount of overlap between the `target` and `source` linestrings can be used to _interpolate attributes_ from the `source` _onto_ the `target` geometries.


:::{.callout-important}
Geometries _must_ be planar—that is in a projected CRS.
:::

```{r example-input}
target_fp <- "https://github.com/JosiahParry/anime/raw/refs/heads/main/r/data-raw/geojson/x_negative.geojson"
source_fp <- "https://github.com/JosiahParry/anime/raw/refs/heads/main/r/data-raw/geojson/y_negative.geojson"

# This is the source data
source_geometry <- sf::read_sf(source_fp) 

# This is the target data, the attributes in the source data will 
# be added to the geometries of the target
target <- sf::read_sf(target_fp) 

plot(sf::st_geometry(source_geometry), col = source_geometry$value)
plot(sf::st_geometry(target), add = TRUE)
```

The lines are parallel but are not identical. The objective of `anime` is to find these partial matches.

```{r}
matches <- anime::anime(
  source = source_geometry,
  target = target,
  distance_tolerance = 0.5,
  angle_tolerance = 5
)

matches_tbl <- get_matches(matches)
matches_tbl
```



We can use this information to join the attributes of the source data to the target data. In this example we take values from `source_geometry` and use `reframe()` to create a new data.frame of interpolated values.

:::{.callout-note}
`interpolate_intensive()` and `interpolate_extensive()` require numeric variables from the `source` and return a numeric vector with the same lengths as `target`.
:::

```{r}
library(dplyr)

# interpolate values
interpolated_from_source <- source_geometry |> 
  reframe(value = interpolate_intensive(value, matches))

# bind them together
interpolated_target <- bind_cols(target, interpolated_from_source)
```

The result can be plotted as follows:

```{r}
plot(interpolated_target["value"])
```

## Example with real data

Imagine the following use case: we want to know how fast traffic moves on roads alongside the Leeds-Bradford cycle superhighway. Notice that the objects are transformed to `EPSG:27700` so that they are in a projected CRS>

```{r}
#| label: cycle_superhighway_input
target_fp <- "https://github.com/nptscot/match_linestrings/releases/download/v0.1/leeds_bradford_cycle_superhighway_linestrings.geojson"
source_fp <- "https://github.com/nptscot/match_linestrings/releases/download/v0.1/leeds_transport_network_near_superhighway.geojson"

target <- sf::read_sf(target_fp) |>
  sf::st_transform(27700)

source_geometry <- sf::read_sf(source_fp) |>
  sf::st_transform(27700) |>
  transmute(value = as.numeric(gsub(" mph", "", maxspeed))) 

plot(sf::st_geometry(target))
plot(source_geometry, add = TRUE)
```


```{r}
#| label: cycle_superhighway_output

# find matches
matches <- anime::anime(
  source = source_geometry,
  target = target,
  # 50 meters distance tolerance 
  distance_tolerance = 50,
  # 10° tolerance 
  angle_tolerance = 10
)

target_interpolated <- target |> 
  mutate(value = interpolate_intensive(source_geometry$value, matches))

summary(source_geometry$value)
summary(target_interpolated$value)
```

```{r}
library(ggplot2)

ggplot() +
  geom_sf(aes(color = value), data = source_geometry, alpha = 0.2) +
  geom_sf(aes(color = value), data = sf::st_crop(target_interpolated, sf::st_bbox(source_geometry)))
```


