# Case Study

This section demonstrates ANIME's practical application through comprehensive case studies using real-world transportation network data. The experiments showcase three distinct attribute transfer scenarios: NPT Scotland cycling network transfer with Go Dutch scenario data, OSM bus route transfer (line-to-line), and speed limit transfer from bus point features to line networks. These cases represent common scenarios in transport planning where different data sources must be integrated to create comprehensive network analyses.

The case studies use the following datasets:

- **NPT.gpkg**: Network Planning Tool Scotland cycling network with Go Dutch scenario data
- **os_networks.gpkg**: Ordnance Survey road network (target network)
- **osm_bus_route.gpkg**: OpenStreetMap bus route data
- **osm_roads.gpkg**: OpenStreetMap road network data (for validation)

Each case demonstrates different aggregation methods and weighting strategies, showcasing ANIME's flexibility in handling diverse attribute transfer requirements.

## Setup and Data Loading

```{r}
#| label: download-data
#| include: false
# Ensure data directory exists and download datasets if missing
data_dir <- "../data"
if (!dir.exists(data_dir)) {
  dir.create(data_dir)
}

datasets <- c(
  "NPT.gpkg", "os_edinburgh.gpkg", "os_glasgow.gpkg",
  "osm_bus_route.gpkg", "osm_edinburgh.gpkg", "osm_glasgow.gpkg"
)

base_url <- "https://github.com/wangzhao0217/anime/releases/download/sample_data"

for (ds in datasets) {
  dest_path <- file.path(data_dir, ds)
  if (!file.exists(dest_path)) {
    message(paste("Downloading", ds, "..."))
    download.file(file.path(base_url, ds), dest_path, mode = "wb")
  }
}
```

```{r}
#| label: setup-case-study
#| include: false
suppressMessages(library(sf))
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))
suppressMessages(library(knitr))
library(sf)
# -----------------------------
# Load pre-prepared datasets
# -----------------------------
os_edinburgh <- sf::st_read("../data/os_edinburgh.gpkg", quiet = TRUE)
os_glasgow <- sf::st_read("../data/os_glasgow.gpkg", quiet = TRUE)
osm_edinburgh <- sf::st_read("../data/osm_edinburgh.gpkg", quiet = TRUE)
osm_glasgow <- sf::st_read("../data/osm_glasgow.gpkg", quiet = TRUE)

# Load NPT and bus route data for Cases 1-2
npt_sf <- sf::st_read("../data/NPT.gpkg", quiet = TRUE)
osm_bus_route_sf <- sf::st_read("../data/osm_bus_route.gpkg", quiet = TRUE)

# Convert multilinestrings to linestrings for ANIME compatibility
osm_edinburgh <- sf::st_cast(osm_edinburgh, "LINESTRING")
osm_glasgow <- sf::st_cast(osm_glasgow, "LINESTRING")
npt_sf <- sf::st_cast(npt_sf, "LINESTRING")
osm_bus_route_sf <- sf::st_cast(osm_bus_route_sf, "LINESTRING")

# Add target IDs for reference
os_edinburgh$target_id <- 1:nrow(os_edinburgh)
os_glasgow$target_id <- 1:nrow(os_glasgow)

# Ensure all datasets are in the same CRS (British National Grid - EPSG:27700)
if(sf::st_crs(npt_sf)$input != "EPSG:27700") {
  npt_sf <- sf::st_transform(npt_sf, 27700)
}
if(sf::st_crs(osm_bus_route_sf)$input != "EPSG:27700") {
  osm_bus_route_sf <- sf::st_transform(osm_bus_route_sf, 27700)
}

# Select target features that overlap with NPT data (for Cases 1-2)
npt_bbox <- sf::st_bbox(npt_sf)
os_in_npt_area <- os_edinburgh[sf::st_intersects(os_edinburgh, sf::st_as_sfc(npt_bbox), sparse = FALSE), ]

# Select 5 sample targets from the overlapping area
if(nrow(os_in_npt_area) >= 5) {
  set.seed(42)
  sample_target_ids <- sample(os_in_npt_area$target_id, 5)
} else if(nrow(os_in_npt_area) > 0) {
  sample_target_ids <- os_in_npt_area$target_id[1:min(5, nrow(os_in_npt_area))]
} else {
  # Fallback: use first 5 targets if no overlap found
  sample_target_ids <- os_edinburgh$target_id[1:5]
}

# -----------------------------
# Validation Data Preparation (Edinburgh)
# -----------------------------
os_names_edin <- unique(na.omit(os_edinburgh$name))
osm_names_edin <- unique(na.omit(osm_edinburgh$name))
common_names <- intersect(os_names_edin, osm_names_edin)

# Create numeric ID lookup table (ANIME requires numerical values)
name_lookup <- data.frame(
  name = common_names,
  name_id = seq_along(common_names),
  stringsAsFactors = FALSE
)

# Assign numeric IDs to each dataset based on road names
os_edinburgh$name_id <- name_lookup$name_id[match(os_edinburgh$name, name_lookup$name)]
osm_edinburgh$name_id <- name_lookup$name_id[match(osm_edinburgh$name, name_lookup$name)]

# Filter to features with common names only for validation
os_valid <- os_edinburgh[!is.na(os_edinburgh$name_id), ]
osm_valid <- osm_edinburgh[!is.na(osm_edinburgh$name_id), ]

# -----------------------------
# Validation Data Preparation (Glasgow)
# -----------------------------
os_names_gla <- unique(na.omit(os_glasgow$name))
osm_names_gla <- unique(na.omit(osm_glasgow$name))
common_names_gla <- intersect(os_names_gla, osm_names_gla)

name_lookup_gla <- data.frame(
  name = common_names_gla,
  name_id = seq_along(common_names_gla),
  stringsAsFactors = FALSE
)

os_glasgow$name_id <- name_lookup_gla$name_id[match(os_glasgow$name, name_lookup_gla$name)]
osm_glasgow$name_id <- name_lookup_gla$name_id[match(osm_glasgow$name, name_lookup_gla$name)]

os_valid_gla <- os_glasgow[!is.na(os_glasgow$name_id), ]
osm_valid_gla <- osm_glasgow[!is.na(osm_glasgow$name_id), ]
```

## Case 1: NPT Scotland Cycling Network Transfer

This case demonstrates the transfer of cycling network attributes from the NPT Scotland cycling network (source) containing Go Dutch scenario data to the OS networks. The `all_fastest_bicycle_go_dutch` attribute represents projected bicycle flow values under the Go Dutch scenario that need to be aggregated using sum aggregation with target-weighted approach.

```{r}
#| label: case1-bicycle-transfer
#| echo: true

# Filter target features for demonstration
target_sample_1 <- os_edinburgh[os_edinburgh$target_id %in% sample_target_ids, ]

# Create mapping from ANIME index to original target_id
target_id_mapping <- data.frame(
  anime_target_id = 1:nrow(target_sample_1),
  original_target_id = target_sample_1$target_id
)

# Run ANIME for Case 1: NPT -> OS Networks
match_matrix_1 <- anime::anime(
  npt_sf,
  target_sample_1,
  distance_tolerance = 15,
  angle_tolerance = 35
)

# Convert to data frame and perform attribute integration
match_df_1 <- as.data.frame(match_matrix_1)

# Map ANIME target_ids back to original target_ids
match_df_1 <- merge(match_df_1, target_id_mapping, by.x = "target_id", by.y = "anime_target_id")
match_df_1$target_id <- match_df_1$original_target_id
match_df_1$original_target_id <- NULL

# Add source attributes
npt_attrs <- st_drop_geometry(npt_sf)
npt_attrs$source_id <- 1:nrow(npt_sf)
match_df_1_attr <- merge(match_df_1, npt_attrs, by = "source_id")

# Bicycle infrastructure transfer using sum aggregation with target weighting
bicycle_transfer <- match_df_1_attr %>%
  group_by(target_id) %>%
  summarise(
    go_dutch = sum(all_fastest_bicycle_go_dutch * target_weighted, na.rm = TRUE),
    .groups = 'drop'
  )

# Integrate results back to target features
target_integrated_1 <- merge(target_sample_1, bicycle_transfer, by = "target_id", all.x = TRUE)
target_integrated_1$go_dutch[is.na(target_integrated_1$go_dutch)] <- 0

print(paste("Case 1: Processed", nrow(match_df_1), "matched pairs for bicycle infrastructure transfer"))
```

```{r}
#| label: table-case1-results
#| echo: false

# Create comparison table for Case 1
if(nrow(match_df_1) > 0 && nrow(match_df_1_attr) > 0) {
  case1_comparison <- match_df_1_attr %>%
    group_by(target_id) %>%
    summarise(
      source_go_dutch_sum = sum(all_fastest_bicycle_go_dutch, na.rm = TRUE),
      n_source_features = n(),
      .groups = 'drop'
    ) %>%
    merge(target_integrated_1[c("target_id", "go_dutch")], by = "target_id") %>%
    mutate(
      difference = go_dutch - source_go_dutch_sum,
      transfer_efficiency = round(go_dutch / source_go_dutch_sum * 100, 1)
    ) %>%
    select(target_id, source_go_dutch_sum, go_dutch, difference, transfer_efficiency, n_source_features)
  
  kable(
    case1_comparison,
    caption = "Case 1: Go Dutch value transfer comparison - Source sum vs Target transferred",
    digits = 2,
    col.names = c("Target ID", "Source Go Dutch Sum", "Target Go Dutch", "Difference", "Transfer Efficiency (%)", "N Source Features")
  )
} else {
  cat("No matches found for Case 1. Try adjusting distance_tolerance or angle_tolerance parameters.")
}
```

## Case 2: Bus Route Transfer

This case demonstrates the transfer of bus route attributes from OSM bus route data to the OS networks. The `route_numerical` attribute is aggregated using mean values with both target and source weighting, then classified as "Yes" or "No" based on the result.

```{r}
#| label: case2-bus-route-transfer
#| echo: true

# Filter target features for demonstration
target_sample_2 <- os_edinburgh[os_edinburgh$target_id %in% sample_target_ids, ]

# Create mapping from ANIME index to original target_id (Case 2)
target_id_mapping_2 <- data.frame(
  anime_target_id = 1:nrow(target_sample_2),
  original_target_id = target_sample_2$target_id
)

# Run ANIME for Case 2: OSM Bus Routes -> OS Networks
match_matrix_2 <- anime::anime(
  osm_bus_route_sf,
  target_sample_2,
  distance_tolerance = 15,
  angle_tolerance = 25
)

# Convert to data frame and perform attribute integration
match_df_2 <- as.data.frame(match_matrix_2)

# Map ANIME target_ids back to original target_ids
if(nrow(match_df_2) > 0) {
  match_df_2 <- merge(match_df_2, target_id_mapping_2, by.x = "target_id", by.y = "anime_target_id")
  match_df_2$target_id <- match_df_2$original_target_id
  match_df_2$original_target_id <- NULL
}

# Add source attributes
bus_route_attrs <- st_drop_geometry(osm_bus_route_sf)
bus_route_attrs$source_id <- 1:nrow(osm_bus_route_sf)
match_df_2_attr <- merge(match_df_2, bus_route_attrs, by = "source_id")

# Bus route transfer using mean aggregation with both target and source weighting
bus_route_transfer <- match_df_2_attr %>%
  group_by(target_id) %>%
  summarise(
    bus_route_mean = sum(route_numerical * target_weighted * source_weighted, na.rm = TRUE) / 
                     sum(target_weighted * source_weighted, na.rm = TRUE),
    .groups = 'drop'
  )

# Classify as Yes/No based on mean value (threshold > 0.5)
bus_route_transfer$bus_route <- ifelse(bus_route_transfer$bus_route_mean > 0.5, "Yes", "No")
bus_route_transfer$bus_route[is.na(bus_route_transfer$bus_route_mean)] <- "No"

# Integrate results back to target features
target_integrated_2 <- merge(target_sample_2, 
                           bus_route_transfer[c("target_id", "bus_route", "bus_route_mean")], 
                           by = "target_id", all.x = TRUE)
target_integrated_2$bus_route[is.na(target_integrated_2$bus_route)] <- "No"

print(paste("Case 2: Processed", nrow(match_df_2), "matched pairs for bus route transfer"))
```

```{r}
#| label: table-case2-results
#| echo: false

# Create comparison table for Case 2
if(nrow(match_df_2) > 0 && nrow(match_df_2_attr) > 0) {
  case2_comparison <- match_df_2_attr %>%
    group_by(target_id) %>%
    summarise(
      source_route_mean = mean(route_numerical, na.rm = TRUE),
      source_route_sum = sum(route_numerical, na.rm = TRUE),
      n_source_features = n(),
      .groups = 'drop'
    ) %>%
    merge(target_integrated_2[c("target_id", "bus_route_mean", "bus_route")], by = "target_id") %>%
    mutate(
      mean_difference = bus_route_mean - source_route_mean
    ) %>%
    select(target_id, source_route_mean, bus_route_mean, mean_difference, bus_route, n_source_features)
  
  kable(
    case2_comparison,
    caption = "Case 2: Bus route value transfer comparison - Source mean vs Target mean with classification",
    digits = 3,
    col.names = c("Target ID", "Source Route Mean", "Target Route Mean", "Mean Difference", "Bus Route (Y/N)", "N Source Features")
  )
} else {
  cat("No matches found for Case 2.")
}
```

## Visualization of Transfer Results

### Case 1: NPT Scotland Cycling Network Transfer

```{r}
#| label: fig-case1-map
#| fig-cap: "Case 1: NPT Scotland cycling network (red, source) matched with OS networks (blue, target)"
#| echo: false

# Get matched source features for visualization
source_indices_1 <- unique(match_df_1$source_id)
source_features_1 <- npt_sf[source_indices_1,]

ggplot() +
  geom_sf(data = source_features_1, color = "red", linewidth = 1) +
  geom_sf(data = target_sample_1, linetype = "dashed", color = "blue", linewidth = 1.2) +
  labs(title = "Case 1: NPT Scotland Cycling Network Transfer") +
  theme_void()
```

### Case 2: Bus Route Transfer

```{r}
#| label: fig-case2-map
#| fig-cap: "Case 2: OSM bus routes (red, source) matched with OS networks (blue, target)"
#| echo: false

# Get matched source features for visualization
source_indices_2 <- unique(match_df_2$source_id)
source_features_2 <- osm_bus_route_sf[source_indices_2,]

ggplot() +
  geom_sf(data = source_features_2, color = "red", linewidth = 1) +
  geom_sf(data = target_sample_2, linetype = "dashed", color = "blue", linewidth = 1.2) +
  labs(title = "Case 2: Bus Route Transfer") +
  theme_void()
```

## Case 3: Attribute Aggregation Validation

This case validates ANIME's attribute transfer accuracy using a controlled experiment. For roads with the same name in both datasets, OSM typically contains multiple linestrings while OS OpenRoads uses a single linestring. We assign random numeric values to OSM features and use ANIME to aggregate them to OS features, then compare against expected aggregations calculated directly from the source data grouped by road name.

This approach tests whether ANIME correctly identifies geometrically corresponding features and aggregates their values appropriately. The comparison reveals how well geometric matching aligns with semantic correspondence (same road name).

```{r}
#| label: case3-validation
#| echo: true

# Set seed for reproducibility
set.seed(42)

# Assign random numeric values to OSM features (simulating an attribute to transfer)
osm_valid$random_value <- runif(nrow(osm_valid), min = 10, max = 100)

# Run ANIME: OSM (source) -> OS (target)
validation_matches <- anime::anime(
  source = osm_valid,
  target = os_valid,
  distance_tolerance = 15,
  angle_tolerance = 15
)

# Transfer random values using extensive interpolation (sum-based)
transferred_extensive <- anime::interpolate_extensive(
  x = osm_valid$random_value,
  matches = validation_matches
)

# Transfer random values using intensive interpolation (weighted mean)
transferred_intensive <- anime::interpolate_intensive(
  x = osm_valid$random_value,
  matches = validation_matches
)

os_valid$transferred_extensive <- transferred_extensive
os_valid$transferred_intensive <- transferred_intensive

print(paste("Case 3: Validation using", length(common_names), "common road names"))
print(paste("OS features for validation:", nrow(os_valid)))
print(paste("OSM features for validation:", nrow(osm_valid)))
```

```{r}
#| label: case3-metrics
#| echo: true

# Calculate expected values by road name (ground truth)
# For extensive: sum of random values per road name
# For intensive: mean of random values per road name
expected_by_name <- osm_valid %>%
  st_drop_geometry() %>%
  group_by(name) %>%
  summarise(
    expected_sum = sum(random_value, na.rm = TRUE),
    expected_mean = mean(random_value, na.rm = TRUE),
    n_osm_features = n(),
    .groups = "drop"
  )

# Join expected values to OS features
os_validation <- os_valid %>%
  st_drop_geometry() %>%
  left_join(expected_by_name, by = "name") %>%
  filter(!is.na(expected_sum) & transferred_extensive > 0)

# Calculate validation metrics
# For extensive interpolation (comparing sums)
mae_extensive <- mean(abs(os_validation$transferred_extensive - os_validation$expected_sum), na.rm = TRUE)
r2_extensive <- cor(os_validation$transferred_extensive, os_validation$expected_sum, use = "complete.obs")^2

# For intensive interpolation (comparing means)
mae_intensive <- mean(abs(os_validation$transferred_intensive - os_validation$expected_mean), na.rm = TRUE)
r2_intensive <- cor(os_validation$transferred_intensive, os_validation$expected_mean, use = "complete.obs")^2

cat("=== Validation Metrics ===\n")
cat(sprintf("Features validated: %d\n", nrow(os_validation)))
cat(sprintf("\nExtensive Interpolation (sum-based):\n"))
cat(sprintf("  R²: %.3f\n", r2_extensive))
cat(sprintf("  MAE: %.2f\n", mae_extensive))
cat(sprintf("\nIntensive Interpolation (mean-based):\n"))
cat(sprintf("  R²: %.3f\n", r2_intensive))
cat(sprintf("  MAE: %.2f\n", mae_intensive))
```

```{r}
#| label: table-case3-results
#| echo: false

# Create validation metrics table
validation_metrics <- data.frame(
  Method = c("Extensive (sum-based)", "Intensive (mean-based)"),
  R_squared = c(sprintf("%.3f", r2_extensive), sprintf("%.3f", r2_intensive)),
  MAE = c(sprintf("%.2f", mae_extensive), sprintf("%.2f", mae_intensive))
)

kable(
  validation_metrics,
  caption = "Case 3: Attribute transfer validation metrics comparing ANIME results against expected aggregations",
  col.names = c("Interpolation Method", "R²", "MAE")
)
```

### Validation Scatter Plot

```{r}
#| label: fig-case3-scatter
#| fig-cap: "Case 3: Scatter plot comparing ANIME transferred values against expected aggregations. Left: Extensive interpolation (sum). Right: Intensive interpolation (mean)."
#| echo: false

library(patchwork)

p1 <- ggplot(os_validation, aes(x = expected_sum, y = transferred_extensive)) +
  geom_point(alpha = 0.5, color = "steelblue") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  labs(
    x = "Expected Sum",
    y = "ANIME Transferred (Extensive)",
    subtitle = sprintf("R² = %.3f", r2_extensive)
  ) +
  theme_minimal()

p2 <- ggplot(os_validation, aes(x = expected_mean, y = transferred_intensive)) +
  geom_point(alpha = 0.5, color = "darkgreen") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  labs(
    x = "Expected Mean",
    y = "ANIME Transferred (Intensive)",
    subtitle = sprintf("R² = %.3f", r2_intensive)
  ) +
  theme_minimal()

p1 + p2
```

## Case 4: Validation Using Road Names as Ground Truth

This case validates ANIME's geometric matching accuracy using road names as ground truth. By encoding road names as unique integer IDs and transferring them via ANIME, we can measure whether geometrically matched features correspond to the same real-world road. If ANIME correctly matches geometries, the transferred road name ID should match the ground truth name in the target dataset.

```{r}
#| label: case4-validation
#| echo: true

# Run ANIME: OSM (source) -> OS (target)
validation_matches_5 <- anime::anime(
  source = osm_valid,
  target = os_valid,
  distance_tolerance = 15,
  angle_tolerance = 15
)

# Transfer name IDs using intensive interpolation (weighted mean)
transferred_name_id <- anime::interpolate_intensive(
  x = osm_valid$name_id,
  matches = validation_matches_5
)

os_valid$transferred_name_id <- transferred_name_id

print(paste("Case 4: Validation using", length(common_names), "common road names"))
print(paste("OS features for validation:", nrow(os_valid)))
print(paste("OSM features for validation:", nrow(osm_valid)))
```

```{r}
#| label: case4-metrics
#| echo: true

# Compare transferred vs ground truth
validation_results_4 <- os_valid %>%
  st_drop_geometry() %>%
  mutate(
    predicted_name_id = round(transferred_name_id),
    has_match = (transferred_name_id > 0),
    match_correct = (predicted_name_id == name_id) & has_match
  )

# Calculate validation metrics
TP <- sum(validation_results_4$match_correct, na.rm = TRUE)
FP <- sum(!validation_results_4$match_correct & validation_results_4$has_match, na.rm = TRUE)
FN <- sum(!validation_results_4$has_match, na.rm = TRUE)

precision <- TP / (TP + FP)
recall <- TP / (TP + FN)
f1_score <- 2 * (precision * recall) / (precision + recall)

cat("=== Validation Metrics ===\n")
cat(sprintf("True Positives (correct matches): %d\n", TP))
cat(sprintf("False Positives (wrong matches): %d\n", FP))
cat(sprintf("False Negatives (missed matches): %d\n", FN))
cat(sprintf("Precision: %.1f%%\n", precision * 100))
cat(sprintf("Recall: %.1f%%\n", recall * 100))
cat(sprintf("F1-Score: %.1f%%\n", f1_score * 100))
```

```{r}
#| label: table-case4-results
#| echo: false

# Create validation metrics table
validation_metrics_5 <- data.frame(
  Metric = c("True Positives", "False Positives", "False Negatives",
             "Precision", "Recall", "F1-Score"),
  Value = c(TP, FP, FN,
            sprintf("%.1f%%", precision * 100),
            sprintf("%.1f%%", recall * 100),
            sprintf("%.1f%%", f1_score * 100))
)

kable(
  validation_metrics_5,
  caption = "Case 4: Validation metrics using road names as ground truth",
  col.names = c("Metric", "Value")
)
```

### Validation Map

```{r}
#| label: fig-case4-map
#| fig-cap: "Case 4: Validation results showing correct matches (green), incorrect matches (red), and unmatched features (gray)"
#| echo: false

# Create validation status for visualization
validation_sf_5 <- os_valid %>%
  mutate(
    predicted_name_id = round(transferred_name_id),
    has_match = (transferred_name_id > 0),
    match_status = case_when(
      !has_match ~ "No Match",
      (predicted_name_id == name_id) ~ "Correct",
      TRUE ~ "Incorrect"
    )
  )

ggplot(validation_sf_5) +
  geom_sf(aes(color = match_status), linewidth = 0.8) +
  scale_color_manual(
    values = c("Correct" = "green3", "Incorrect" = "red", "No Match" = "gray60"),
    name = "Match Status"
  ) +
  labs(
    title = "ANIME Validation: Road Name Transfer Accuracy",
    subtitle = sprintf("Precision: %.1f%%, Recall: %.1f%%, F1: %.1f%%",
                       precision * 100, recall * 100, f1_score * 100)
  ) +
  theme_minimal()
```

## Case 5: Parameter Sensitivity Analysis

This case examines how ANIME's matching accuracy varies with different parameter settings. By systematically testing combinations of `distance_tolerance` (5-30m) and `angle_tolerance` (5-45°), we identify optimal parameter ranges and understand the algorithm's sensitivity to these settings.

```{r}
#| label: case5-sensitivity
#| echo: true

# Define parameter grid
distance_values <- c(5, 10, 15, 20, 25, 30)
angle_values <- c(5, 10, 15, 20, 25, 30, 35, 40, 45)

sensitivity_results <- expand.grid(
  distance_tolerance = distance_values,
  angle_tolerance = angle_values,
  precision = NA_real_,
  recall = NA_real_,
  f1_score = NA_real_,
  n_matches = NA_integer_
)

# Run ANIME for each parameter combination
for (i in seq_len(nrow(sensitivity_results))) {
  dt <- sensitivity_results$distance_tolerance[i]
  at <- sensitivity_results$angle_tolerance[i]

  # Run ANIME with current parameters
  matches_i <- anime::anime(
    source = osm_valid,
    target = os_valid,
    distance_tolerance = dt,
    angle_tolerance = at
  )

  # Transfer name IDs using intensive interpolation
  transferred_i <- anime::interpolate_intensive(
    x = osm_valid$name_id,
    matches = matches_i
  )

  # Calculate validation metrics
  predicted_i <- round(transferred_i)
  has_match_i <- (transferred_i > 0)
  match_correct_i <- (predicted_i == os_valid$name_id) & has_match_i

  TP_i <- sum(match_correct_i, na.rm = TRUE)
  FP_i <- sum(!match_correct_i & has_match_i, na.rm = TRUE)
  FN_i <- sum(!has_match_i, na.rm = TRUE)

  prec_i <- if ((TP_i + FP_i) > 0) TP_i / (TP_i + FP_i) else 0
  rec_i <- if ((TP_i + FN_i) > 0) TP_i / (TP_i + FN_i) else 0
  f1_i <- if ((prec_i + rec_i) > 0) 2 * prec_i * rec_i / (prec_i + rec_i) else 0

  sensitivity_results$precision[i] <- prec_i
  sensitivity_results$recall[i] <- rec_i
  sensitivity_results$f1_score[i] <- f1_i
  sensitivity_results$n_matches[i] <- TP_i + FP_i
}

print(paste("Case 5: Tested", nrow(sensitivity_results), "parameter combinations"))
```

```{r}
#| label: table-case5-results
#| echo: false

# Create summary table of best parameters
best_f1_idx <- which.max(sensitivity_results$f1_score)
best_params <- sensitivity_results[best_f1_idx, ]

cat(sprintf("Best F1-Score: %.1f%% at distance_tolerance=%dm, angle_tolerance=%d°\n",
            best_params$f1_score * 100,
            best_params$distance_tolerance,
            best_params$angle_tolerance))

# Show top 5 parameter combinations
top_5 <- sensitivity_results[order(-sensitivity_results$f1_score), ][1:5, ]
kable(
  top_5,
  caption = "Case 5: Top 5 parameter combinations by F1-Score",
  digits = 3,
  col.names = c("Distance (m)", "Angle (°)", "Precision", "Recall", "F1-Score", "N Matches")
)
```

### Sensitivity Heatmap

```{r}
#| label: fig-case5-heatmap
#| fig-cap: "Case 5: F1-Score heatmap showing ANIME matching accuracy across parameter combinations. Higher values (yellow) indicate better matching performance."
#| echo: false

ggplot(sensitivity_results, aes(x = factor(distance_tolerance),
                                 y = factor(angle_tolerance),
                                 fill = f1_score)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%.1f%%", f1_score * 100)),
            color = "black", size = 3) +
  scale_fill_viridis_c(name = "F1-Score",
                       limits = c(min(sensitivity_results$f1_score) * 0.95, 1),
                       option = "plasma") +
  labs(
    x = "Distance Tolerance (m)",
    y = "Angle Tolerance (°)",
    title = "Parameter Sensitivity Analysis"
  ) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    axis.text = element_text(size = 10)
  )
```

### Precision-Recall Trade-off

```{r}
#| label: fig-case5-tradeoff
#| fig-cap: "Case 5: Precision vs Recall trade-off across parameter combinations. Point size indicates distance tolerance, color indicates angle tolerance."
#| echo: false

ggplot(sensitivity_results, aes(x = recall, y = precision,
                                 size = distance_tolerance,
                                 color = factor(angle_tolerance))) +
  geom_point(alpha = 0.7) +
  scale_size_continuous(name = "Distance (m)", range = c(3, 8)) +
  scale_color_viridis_d(name = "Angle (°)", option = "turbo") +
  labs(
    x = "Recall",
    y = "Precision",
    title = "Precision-Recall Trade-off"
  ) +
  theme_minimal() +
  coord_cartesian(xlim = c(0.5, 1), ylim = c(0.5, 1))
```

## Case 6: Statistical Validation with Bootstrap Confidence Intervals

This case enhances the validation from Case 4 by providing bootstrap confidence intervals for the validation metrics, demonstrating the statistical robustness of ANIME's matching accuracy.

```{r}
#| label: case6-bootstrap-validation
#| echo: true

# Bootstrap confidence intervals for validation metrics
set.seed(42)
n_bootstrap <- 1000

# Reuse validation matches from Case 4
validation_matches_7 <- anime::anime(
  source = osm_valid,
  target = os_valid,
  distance_tolerance = 15,
  angle_tolerance = 15
)

# Prepare data for bootstrap
validation_data_7 <- os_valid %>%
  st_drop_geometry() %>%
  mutate(
    transferred = anime::interpolate_intensive(osm_valid$name_id, validation_matches_7),
    predicted = round(transferred),
    has_match = (transferred > 0),
    match_correct = (predicted == name_id) & has_match
  )

# Function to calculate metrics for bootstrap
calc_metrics <- function(data, indices) {
  d <- data[indices, ]
  TP <- sum(d$match_correct, na.rm = TRUE)
  FP <- sum(!d$match_correct & d$has_match, na.rm = TRUE)
  FN <- sum(!d$has_match, na.rm = TRUE)

  precision <- if ((TP + FP) > 0) TP / (TP + FP) else 0
  recall <- if ((TP + FN) > 0) TP / (TP + FN) else 0
  f1 <- if ((precision + recall) > 0) 2 * precision * recall / (precision + recall) else 0

  c(precision = precision, recall = recall, f1 = f1)
}

# Run bootstrap
library(boot)
boot_results <- boot(validation_data_7, calc_metrics, R = n_bootstrap)

# Calculate 95% confidence intervals
ci_precision <- boot.ci(boot_results, type = "perc", index = 1)
ci_recall <- boot.ci(boot_results, type = "perc", index = 2)
ci_f1 <- boot.ci(boot_results, type = "perc", index = 3)

cat("=== Bootstrap Validation Results (n=1000) ===\n")
cat(sprintf("Precision: %.1f%% [95%% CI: %.1f%% - %.1f%%]\n",
            mean(boot_results$t[,1]) * 100,
            ci_precision$percent[4] * 100,
            ci_precision$percent[5] * 100))
cat(sprintf("Recall: %.1f%% [95%% CI: %.1f%% - %.1f%%]\n",
            mean(boot_results$t[,2]) * 100,
            ci_recall$percent[4] * 100,
            ci_recall$percent[5] * 100))
cat(sprintf("F1-Score: %.1f%% [95%% CI: %.1f%% - %.1f%%]\n",
            mean(boot_results$t[,3]) * 100,
            ci_f1$percent[4] * 100,
            ci_f1$percent[5] * 100))
```

```{r}
#| label: table-case6-bootstrap
#| echo: false

# Create bootstrap results table
bootstrap_table <- data.frame(
  Metric = c("Precision", "Recall", "F1-Score"),
  Mean = c(
    sprintf("%.1f%%", mean(boot_results$t[,1]) * 100),
    sprintf("%.1f%%", mean(boot_results$t[,2]) * 100),
    sprintf("%.1f%%", mean(boot_results$t[,3]) * 100)
  ),
  CI_Lower = c(
    sprintf("%.1f%%", ci_precision$percent[4] * 100),
    sprintf("%.1f%%", ci_recall$percent[4] * 100),
    sprintf("%.1f%%", ci_f1$percent[4] * 100)
  ),
  CI_Upper = c(
    sprintf("%.1f%%", ci_precision$percent[5] * 100),
    sprintf("%.1f%%", ci_recall$percent[5] * 100),
    sprintf("%.1f%%", ci_f1$percent[5] * 100)
  )
)

kable(
  bootstrap_table,
  caption = "Case 6: Bootstrap validation metrics with 95% confidence intervals (n=1,000 resamples)",
  col.names = c("Metric", "Mean", "95% CI Lower", "95% CI Upper")
)
```

### Stratified Analysis by Road Classification

```{r}
#| label: case6-stratified
#| echo: true

# Stratify by road classification
stratified_results <- os_valid %>%
  st_drop_geometry() %>%
  mutate(
    transferred = anime::interpolate_intensive(osm_valid$name_id, validation_matches_7),
    predicted = round(transferred),
    has_match = (transferred > 0),
    match_correct = (predicted == name_id) & has_match
  ) %>%
  group_by(road_function) %>%
  summarise(
    n_features = n(),
    TP = sum(match_correct, na.rm = TRUE),
    FP = sum(!match_correct & has_match, na.rm = TRUE),
    FN = sum(!has_match, na.rm = TRUE),
    precision = round(TP / (TP + FP), 3),
    recall = round(TP / (TP + FN), 3),
    f1 = round(2 * precision * recall / (precision + recall), 3),
    .groups = "drop"
  )

kable(
  stratified_results,
  caption = "Case 6: Validation metrics stratified by road function",
  col.names = c("Road Function", "N Features", "TP", "FP", "FN", "Precision", "Recall", "F1-Score")
)
```

## Case 7: Comparative Benchmarking Against Baseline Methods

This case compares ANIME's matching performance against three baseline methods: buffer-based matching, Hausdorff distance matching, and nearest neighbor matching.

```{r}
#| label: case7-baseline-methods
#| echo: true

# === BASELINE METHOD 1: Buffer-based matching ===
buffer_match <- function(source, target, buffer_dist) {
  start_time <- Sys.time()
  source_buffered <- st_buffer(source, buffer_dist)
  intersects <- st_intersects(source_buffered, target)
  matches <- data.frame(
    source_id = rep(seq_along(intersects), lengths(intersects)),
    target_id = unlist(intersects)
  )
  runtime <- as.numeric(difftime(Sys.time(), start_time, units = "secs"))
  list(matches = matches, runtime = runtime)
}

# === BASELINE METHOD 2: Nearest neighbor matching ===
nn_match <- function(source, target) {
  start_time <- Sys.time()
  nearest <- st_nearest_feature(source, target)
  matches <- data.frame(
    source_id = seq_along(nearest),
    target_id = nearest
  )
  runtime <- as.numeric(difftime(Sys.time(), start_time, units = "secs"))
  list(matches = matches, runtime = runtime)
}

# Use subset for comparison
sample_size <- min(200, nrow(osm_valid))
osm_sample <- osm_valid[1:sample_size, ]
os_sample <- os_valid[1:sample_size, ]

print(paste("Case 7: Comparing methods on", sample_size, "features"))
```

```{r}
#| label: case7-run-methods
#| echo: true

# Run ANIME
anime_start <- Sys.time()
anime_matches_8 <- anime::anime(osm_sample, os_sample, 15, 15)
anime_runtime <- as.numeric(difftime(Sys.time(), anime_start, units = "secs"))

# Run Buffer
buffer_result <- buffer_match(osm_sample, os_sample, 15)

# Run Nearest Neighbor
nn_result <- nn_match(osm_sample, os_sample)

print(paste("ANIME runtime:", round(anime_runtime, 3), "s"))
print(paste("Buffer runtime:", round(buffer_result$runtime, 3), "s"))
print(paste("NN runtime:", round(nn_result$runtime, 3), "s"))
```

```{r}
#| label: case7-evaluation
#| echo: true

# Function to evaluate matches against ground truth
evaluate_matches <- function(matches_df, source_data, target_data) {
  if (nrow(matches_df) == 0) return(c(precision = NA, recall = NA, f1 = NA))
  matches_df$source_name_id <- source_data$name_id[matches_df$source_id]
  matches_df$target_name_id <- target_data$name_id[matches_df$target_id]
  correct <- sum(matches_df$source_name_id == matches_df$target_name_id, na.rm = TRUE)
  total_matches <- nrow(matches_df)
  total_possible <- nrow(target_data)
  precision <- correct / total_matches
  recall <- correct / total_possible
  f1 <- 2 * precision * recall / (precision + recall)
  c(precision = precision, recall = recall, f1 = f1)
}

# Evaluate all methods
anime_df_8 <- as.data.frame(anime_matches_8)
anime_metrics <- evaluate_matches(anime_df_8, osm_sample, os_sample)
buffer_metrics <- evaluate_matches(buffer_result$matches, osm_sample, os_sample)
nn_metrics <- evaluate_matches(nn_result$matches, osm_sample, os_sample)
```

```{r}
#| label: table-case7-comparison
#| echo: false

comparison_table <- data.frame(
  Method = c("ANIME", "Buffer (15m)", "Nearest Neighbor"),
  Precision = c(anime_metrics["precision"], buffer_metrics["precision"], nn_metrics["precision"]),
  Recall = c(anime_metrics["recall"], buffer_metrics["recall"], nn_metrics["recall"]),
  F1_Score = c(anime_metrics["f1"], buffer_metrics["f1"], nn_metrics["f1"]),
  Runtime_s = c(anime_runtime, buffer_result$runtime, nn_result$runtime)
)

kable(
  comparison_table,
  caption = "Case 7: Comparative benchmarking of matching methods",
  digits = 3,
  col.names = c("Method", "Precision", "Recall", "F1-Score", "Runtime (s)")
)
```

## Case 8: Failure Mode Analysis

This case analyzes the patterns of matching errors to identify systematic failure modes and provide guidance for practitioners.

```{r}
#| label: case8-error-analysis
#| echo: true

# Identify false positives and false negatives
validation_results_8 <- os_valid %>%
  mutate(
    transferred = anime::interpolate_intensive(osm_valid$name_id, validation_matches_7),
    predicted = round(transferred),
    has_match = (transferred > 0),
    match_correct = (predicted == name_id) & has_match,
    error_type = case_when(
      match_correct ~ "True Positive",
      has_match & !match_correct ~ "False Positive",
      !has_match ~ "False Negative",
      TRUE ~ "Unknown"
    )
  )

# Analyze error patterns
error_summary <- validation_results_8 %>%
  st_drop_geometry() %>%
  group_by(error_type) %>%
  summarise(
    count = n(),
    pct = round(n() / nrow(validation_results_8) * 100, 1),
    .groups = "drop"
  )

print("=== Error Distribution ===")
print(error_summary)
```

```{r}
#| label: case8-complexity
#| echo: true

# Analyze by geometry complexity (number of vertices)
validation_results_8$n_vertices <- sapply(
  st_geometry(validation_results_8),
  function(x) nrow(st_coordinates(x))
)

complexity_analysis <- validation_results_8 %>%
  st_drop_geometry() %>%
  mutate(complexity = cut(n_vertices,
    breaks = c(0, 2, 5, 10, Inf),
    labels = c("Simple (2)", "Low (3-5)", "Medium (6-10)", "High (>10)")
  )) %>%
  group_by(complexity, error_type) %>%
  summarise(count = n(), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = error_type, values_from = count, values_fill = 0)

print("=== Error by Geometry Complexity ===")
print(complexity_analysis)
```

```{r}
#| label: table-case8-errors
#| echo: false

kable(
  error_summary,
  caption = "Case 8: Distribution of matching errors",
  col.names = c("Error Type", "Count", "Percentage (%)")
)
```

```{r}
#| label: table-case8-complexity
#| echo: false

kable(
  complexity_analysis,
  caption = "Case 8: Error distribution by geometry complexity"
)
```

## Case 9: Geographic Generalizability - Glasgow Validation

This case validates ANIME's performance on a second city with different urban morphology to demonstrate geographic generalizability. Glasgow, Scotland's largest city, features a more regular grid-like street pattern in its center compared to Edinburgh's medieval organic layout, providing a contrasting test environment.

```{r}
#| label: case9-glasgow-data
#| echo: true
#| message: false

# Use pre-prepared Glasgow data (loaded in setup chunk)
print(paste("Glasgow OS features:", nrow(os_glasgow)))
print(paste("Glasgow OSM features:", nrow(osm_glasgow)))
print(paste("Glasgow OS features for validation:", nrow(os_valid_gla)))
print(paste("Glasgow OSM features for validation:", nrow(osm_valid_gla)))
```

```{r}
#| label: case9-glasgow-validation
#| echo: true

# Use pre-prepared Glasgow validation data (created in setup chunk)
# os_valid_gla and osm_valid_gla already have name_id assigned

print(paste("Glasgow OS features for validation:", nrow(os_valid_gla)))
print(paste("Glasgow OSM features for validation:", nrow(osm_valid_gla)))
```

```{r}
#| label: case9-glasgow-metrics
#| echo: true

# Run ANIME on Glasgow data using pre-prepared validation datasets
glasgow_matches <- anime::anime(
  source = osm_valid_gla,
  target = os_valid_gla,
  distance_tolerance = 15,
  angle_tolerance = 15
)

# Transfer name IDs
glasgow_transferred <- anime::interpolate_intensive(
  x = osm_valid_gla$name_id,
  matches = glasgow_matches
)

# Calculate validation metrics
glasgow_results <- os_valid_gla %>%
  st_drop_geometry() %>%
  mutate(
    transferred = glasgow_transferred,
    predicted = round(transferred),
    has_match = (transferred > 0),
    match_correct = (predicted == name_id) & has_match
  )

TP_g <- sum(glasgow_results$match_correct, na.rm = TRUE)
FP_g <- sum(!glasgow_results$match_correct & glasgow_results$has_match, na.rm = TRUE)
FN_g <- sum(!glasgow_results$has_match, na.rm = TRUE)

precision_g <- TP_g / (TP_g + FP_g)
recall_g <- TP_g / (TP_g + FN_g)
f1_g <- 2 * (precision_g * recall_g) / (precision_g + recall_g)

cat("=== Glasgow Validation Metrics ===\n")
cat(sprintf("True Positives: %d\n", TP_g))
cat(sprintf("False Positives: %d\n", FP_g))
cat(sprintf("False Negatives: %d\n", FN_g))
cat(sprintf("Precision: %.1f%%\n", precision_g * 100))
cat(sprintf("Recall: %.1f%%\n", recall_g * 100))
cat(sprintf("F1-Score: %.1f%%\n", f1_g * 100))
```

```{r}
#| label: table-case9-comparison
#| echo: false

# Compare Edinburgh vs Glasgow results
city_comparison <- data.frame(
  City = c("Edinburgh", "Glasgow"),
  Precision = c(sprintf("%.1f%%", precision * 100), sprintf("%.1f%%", precision_g * 100)),
  Recall = c(sprintf("%.1f%%", recall * 100), sprintf("%.1f%%", recall_g * 100)),
  F1_Score = c(sprintf("%.1f%%", f1_score * 100), sprintf("%.1f%%", f1_g * 100)),
  Urban_Pattern = c("Medieval organic", "Grid-like center")
)

kable(
  city_comparison,
  caption = "Case 9: Comparison of ANIME validation metrics across cities with different urban morphologies",
  col.names = c("City", "Precision", "Recall", "F1-Score", "Urban Pattern")
)
```

## Summary of Results

The nine case studies demonstrate ANIME's versatility in handling different types of attribute transfer scenarios:

**Case 1** successfully transferred NPT Scotland cycling network Go Dutch scenario values using sum aggregation with target weighting, preserving the cumulative nature of projected bicycle flow data across network segments.

**Case 2** demonstrated categorical classification capabilities by transferring bus route data using mean aggregation with dual weighting, then applying a threshold-based classification to produce binary Yes/No results.

**Case 3** provided quantitative validation of ANIME's attribute transfer accuracy using a controlled experiment with random values. By comparing ANIME's aggregated results against expected values calculated from source data grouped by road name, this case demonstrates that ANIME achieves reliable attribute transfer.

**Case 4** validated ANIME's geometric matching accuracy using road names as ground truth. By encoding road names as numeric IDs and comparing transferred values against known ground truth, this case demonstrates that ANIME achieves high precision and recall in identifying corresponding features.

**Case 5** provided parameter sensitivity analysis examining how `distance_tolerance` and `angle_tolerance` affect matching accuracy. The heatmap visualization reveals optimal parameter ranges and demonstrates the algorithm's robustness across different settings.

**Case 6** enhanced validation rigor by providing bootstrap confidence intervals for precision, recall, and F1-score metrics, demonstrating the statistical robustness of ANIME's matching accuracy.

**Case 7** compared ANIME against baseline methods (buffer-based and nearest neighbor matching), demonstrating ANIME's superior precision through its angle-constrained matching approach.

**Case 8** analyzed failure modes by categorizing matching errors and examining their relationship to geometry complexity, providing practical guidance for practitioners.

**Case 9** validated ANIME's geographic generalizability by testing on Glasgow, a city with different urban morphology (grid-like center) compared to Edinburgh's medieval organic layout. Consistent performance across both cities demonstrates the algorithm's robustness to varying street network patterns.

Each case utilized different combinations of weighting strategies and aggregation functions, illustrating ANIME's flexibility in accommodating diverse analytical requirements in transportation network integration tasks.

```{r}
#| label: table-summary-stats
#| echo: false
summary_stats <- data.frame(
  Case = c("NPT Scotland Cycling Network", "Bus Route Transfer", "Attribute Aggregation Validation", "Road Name Validation", "Parameter Sensitivity", "Bootstrap Validation", "Comparative Benchmarking", "Failure Mode Analysis", "Glasgow Generalizability"),
  Source_Type = c("Line (NPT)", "Line (OSM Bus Routes)", "Line (OSM Roads)", "Line (OSM Roads)", "Line (OSM Roads)", "Line (OSM Roads)", "Line (OSM Roads)", "Line (OSM Roads)", "Line (Glasgow OSM)"),
  Target_Type = c("Line (OS Networks)", "Line (OS Networks)", "Line (OS Networks)", "Line (OS Networks)", "Line (OS Networks)", "Line (OS Networks)", "Line (OS Networks)", "Line (OS Networks)", "Line (Glasgow OSM)"),
  Aggregation = c("Sum", "Mean → Classification", "Extensive + Intensive", "Intensive (Name ID)", "Intensive (Name ID)", "Bootstrap CI", "Multiple Methods", "Error Analysis", "Intensive (Name ID)"),
  Weights = c("Target", "Target + Source", "Target", "Target", "Target", "Target", "Target", "Target", "Target"),
  Matches_Found = c(nrow(match_df_1), nrow(match_df_2), nrow(os_validation), TP + FP, nrow(sensitivity_results), n_bootstrap, sample_size, nrow(validation_results_8), TP_g + FP_g)
)

kable(
  summary_stats,
  caption = "Summary of case study configurations and results"
)
```